Spinal Atomic Lambda-Calculus

### 2020-04-06 3 - FoSSaCS 2020 (Final)/SALC.tex
names "fixed"

\begin{document}
%
\title{Spinal Atomic Lambda-Calculus}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Tom Gundersen\inst{1} \and
Willem Heijltjes\inst{2}\and
Michel Parigot\inst{3} \and
David Sherratt\inst{4} (\Letter)}
%
\authorrunning{Gundersen et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
        Red Hat, Inc. \\ \email{teg@jklm.no} 
\\ \and	University of Bath, UK \\ \email{w.b.heijltjes@bath.ac.uk}
\\ \and Institut de Recherche en Informatique Fondamentale, CNRS, Universit\'e de Paris \\ \email{parigot@irif.fr}
\\ \and Friedrich-Schiller-Universit\"{a}t Jena, Germany \\ \email{david.rhys.sherratt@uni-jena.de}}
%
\maketitle              % typeset the header of the contribution
%
\vspace{-1cm}
\blfootnote{This work was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing} and ANR project 15-CE25-0014 \emph{The Fine Structure of Formal Proof Systems and their Computational Interpretations (FISP)}}

>>>>

\begin{document}
%
\title{Spinal Atomic Lambda-Calculus}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Tom Gundersen\inst{1} \and
Willem Heijltjes\inst{2}\and
Michel Parigot\inst{3} \and
David Sherratt\inst{4} (\Letter)}
%
\authorrunning{Sherratt et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
        Friedrich-Schiller-Universit\"{a}t Jena, Germany \\ \email{david.rhys.sherratt@uni-jena.de}
\\ \and	University of Bath, UK. \\ \email{w.b.heijltjes@bath.ac.uk}
\\ \and Red Hat, Inc. Norway.   \\ \email{teg@jklm.no} 
\\ \and Institut de Recherche en Informatique Fondamentale, CNRS, Universit\'e de Paris. France. \\ \email{parigot@irif.fr}
}
%
\maketitle              % typeset the header of the contribution
%
\vspace{-1cm}
\blfootnote{This work was supported by EPSRC Project EP/R029121/1 \emph{Typed Lambda-Calculi with Sharing and Unsharing} and ANR project 15-CE25-0014 \emph{The Fine Structure of Formal Proof Systems and their Computational Interpretations (FISP)}}
